Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-02-25 article-models-tt.tex
reorganizing the notes

\subsubsection{Extension on terms}
When $\jterm{\Gamma}{A}{x}$ and $\jterm{\Gamma}{\subst{x}{P}}{u}$ are terms,
we obtain a term $\jterm{\Gamma}{\ctxext{A}{P}}{\ctxext{x}{u}}$. This operation
of weakening on terms is like the pairing operation. However, it is handled
much stricter for it has a judgmental inverse and it is subject to various compatibility
rules.
\begin{align}
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jterm{\Gamma}{\ctxext{A}{P}}{\ctxext{x}{u}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jterm{\Gamma}{A}{\pts{w}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jterm{\Gamma}{\subst{\pts{w}}{P}}{\edg{w}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jtermeq{\Gamma}{\ctxext{A}{P}}{\ctxext{\pts{w}}{\edg{w}}}{w}}\\
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jtermeq{\Gamma}{A}{\pts{(\ctxext{x}{u})}}{x}}\\
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jtermeq{\Gamma}{\subst{x}{P}}{\edg{(\ctxext{x}{u})}}{u}}
\end{align}

>>>>

\subsubsection{Extension on terms}
When $\jterm{\Gamma}{A}{x}$ and $\jterm{\Gamma}{\subst{x}{P}}{u}$ are terms,
we obtain a term $\jterm{\Gamma}{\ctxext{A}{P}}{\ctxext{x}{u}}$. This operation
of weakening on terms is like the pairing operation and like with the pairing
operation, extension on terms tells what the terms of an extended family are. 
However, it is handled
much stricter than $\smsym$-types, 
for it has a judgmental inverse and it is subject to various compatibility
rules.
\begin{align}
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jterm{\Gamma}{\ctxext{A}{P}}{\ctxext{x}{u}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jterm{\Gamma}{A}{\pts{w}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jterm{\Gamma}{\subst{\pts{w}}{P}}{\edg{w}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jtermeq{\Gamma}{\ctxext{A}{P}}{\ctxext{\pts{w}}{\edg{w}}}{w}}\\
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jtermeq{\Gamma}{A}{\pts{(\ctxext{x}{u})}}{x}}\\
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jtermeq{\Gamma}{\subst{x}{P}}{\edg{(\ctxext{x}{u})}}{u}}
\end{align}
